%% Declaration of Interests for Neurocomputing Submission

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{amssymb}

\begin{document}

\title{\textbf{Declaration of Interests}}
\date{}
\maketitle

$\square$ The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.

$\boxtimes$ The authors declare the following financial interests/personal relationships which may be considered as potential competing interests:

S. Niu reports financial support was provided by National Natural Science Foundation of China (Grant No. 62471202, 62302191). S. Niu reports financial support was provided by Natural Science Foundation of Shandong Province (Grant No. ZR2023QF001). S. Niu reports financial support was provided by Development Program Project of Youth Innovation Team of Institutions of Higher Learning in Shandong Province (Grant No. 2023KJ315). S. Niu reports financial support was provided by Young Talent of Lifting Engineering for Science and Technology in Shandong (Grant No. SDAST2024QTA014). S. Niu reports a relationship with Key Laboratory of Intelligent Computing Technology for Network Environment, Shandong Province, School of Information Science and Engineering, University of Jinan that includes: funding grants. If there are other authors, they declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.

\end{document}
